Associations_PFN_Cognition

### 2023-04-12 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
sensitivity analyses

combined.data <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
```

## Import the Thompson PC scores from DEAP
```{r}
newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data)))],by="subjectkey")

# for simplicity, rename thompson variables
colnames(all.data)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data))
```

@@

# standardize all variables for LMER (separately in Discovery and Replication samples)
```{r}
abcd.data.train.harmonized$PFN3<-(abcd.data.train.harmonized$PFN3-mean(abcd.data.train.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN3,na.rm=TRUE)

abcd.data.train.harmonized$PFN15<-(abcd.data.train.harmonized$PFN15-mean(abcd.data.train.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN15,na.rm=TRUE)

abcd.data.train.harmonized$PFN17<-(abcd.data.train.harmonized$PFN17-mean(abcd.data.train.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN17,na.rm=TRUE)

abcd.data.test.harmonized$PFN3<-(abcd.data.test.harmonized$PFN3-mean(abcd.data.test.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN3,na.rm=TRUE)

abcd.data.test.harmonized$PFN15<-(abcd.data.test.harmonized$PFN15-mean(abcd.data.test.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN15,na.rm=TRUE)

abcd.data.test.harmonized$PFN17<-(abcd.data.test.harmonized$PFN17-mean(abcd.data.test.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN17,na.rm=TRUE)

abcd.data.train.harmonized$interview_age<-(abcd.data.train.harmonized$interview_age-mean(abcd.data.train.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.train.harmonized$interview_age,na.rm=TRUE)

abcd.data.test.harmonized$interview_age<-(abcd.data.test.harmonized$interview_age-mean(abcd.data.test.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.test.harmonized$interview_age,na.rm=TRUE)

abcd.data.train.harmonized$meanFD<-(abcd.data.train.harmonized$meanFD-mean(abcd.data.train.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.train.harmonized$meanFD,na.rm=TRUE)

abcd.data.test.harmonized$meanFD<-(abcd.data.test.harmonized$meanFD-mean(abcd.data.test.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.test.harmonized$meanFD,na.rm=TRUE)

@@

tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Replication.doc")
```

@@

# Make a demographics table
```{r}
# exclude subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]

abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]

library(Gmisc)
demo_table <- abcd.data.traintest %>%
  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
#subset(matched_group<3) %>%
  set_column_labels(interview_age = "Age (Months)",
                    sex = "Sex",
                    race.6level = "Race",
                    household.income = "Household Income",
                    thompson_PC1 = "General Cognition",
                    thompson_PC2 = "Executive Function",
                    thompson_PC3 = "Learning/Memory",
                    high.educ = "Parent Education") %>%
getDescriptionStatsBy(interview_age, 
                        sex,
                        thompson_PC1,
                        thompson_PC2,
                        thompson_PC3,
                        household.income,
                        race.6level,
                        high.educ,
                        add_total_col = TRUE, statistics=TRUE,
                        by = matched_group)

@@

@@

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_train)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- c("dashed", "solid", "solid", "solid", "dashed", "dashed",
              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
              "dashed", "dashed", "solid", "dashed", "solid");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=c("#FFFFFF", "#7499C2", "#F5BA2E",
                                     "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + 
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,2,11,10,1,9,5,16,14,12,7,8,13,6,3,15,17)]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = c('4','2','11','10','1','9','5','16','14','12','7','8','13','6','3','15','17'),limits = c('5','2','15','1','7','14','11','12','6','4','3','10','13','9','16','8','17')) 
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_test)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- c("dashed", "dashed", "solid", "solid", "dashed", "solid",
              "dashed", "dashed", "dashed", "dashed", "dashed", "dashed",
              "dashed", "dashed", "solid", "dashed", "solid");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=c("#FFFFFF", "#FFFFFF", "#F5BA2E",
                                     "#7499C2", "#FFFFFF", "#AF33AD", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                                     "#FFFFFF", "#F5BA2E", "#FFFFFF", "#F5BA2E"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + 
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[c(4,13,9,2,7,12,10,5,16,14,8,1,11,3,15,17,6)]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = c('4','13','9','2','7','12','10','5','16','14','8','1','11','3','15','17','6'),limits = c('12','4','14','1','8','17','5','11','3','7','13','6','2','10','15','9','16')) # + scale_y_continuous(limits = c(-4, 6), breaks = c(-4, -2, 0, 2, 4, 6));
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_test.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@

>>>>

combined.data1 <- merge(data.clean,abcd_imgincl01[, c("subjectkey",'imgincl_t1w_include')],by="subjectkey") 
```

## Import the Thompson PC scores from DEAP
```{r}
newdata<-readRDS("/Users/askeller/Documents/Kellernet_PrelimAnalysis/DEAP-data-download_ThompsonScores_ResFamIncome.rds")
newdata.baseline<-newdata[newdata$event_name=="baseline_year_1_arm_1",]
colnames(newdata.baseline)[1]<-"subjectkey"
all.data <- merge(combined.data1,newdata.baseline[,c("subjectkey", setdiff(colnames(newdata.baseline),colnames(combined.data1)))],by="subjectkey")

# for simplicity, rename thompson variables
colnames(all.data)<-gsub("neurocog_pc1.bl","thompson_PC1",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc2.bl","thompson_PC2",colnames(all.data))
colnames(all.data)<-gsub("neurocog_pc3.bl","thompson_PC3",colnames(all.data))

@@

# standardize all variables for LMER (separately in Discovery and Replication samples)
```{r}
abcd.data.train.harmonized$PFN1<-(abcd.data.train.harmonized$PFN1-mean(abcd.data.train.harmonized$PFN1,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN1,na.rm=TRUE)
abcd.data.train.harmonized$PFN2<-(abcd.data.train.harmonized$PFN2-mean(abcd.data.train.harmonized$PFN2,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN2,na.rm=TRUE)
abcd.data.train.harmonized$PFN3<-(abcd.data.train.harmonized$PFN3-mean(abcd.data.train.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN3,na.rm=TRUE)
abcd.data.train.harmonized$PFN4<-(abcd.data.train.harmonized$PFN4-mean(abcd.data.train.harmonized$PFN4,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN4,na.rm=TRUE)
abcd.data.train.harmonized$PFN5<-(abcd.data.train.harmonized$PFN5-mean(abcd.data.train.harmonized$PFN5,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN5,na.rm=TRUE)
abcd.data.train.harmonized$PFN6<-(abcd.data.train.harmonized$PFN6-mean(abcd.data.train.harmonized$PFN6,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN6,na.rm=TRUE)
abcd.data.train.harmonized$PFN7<-(abcd.data.train.harmonized$PFN7-mean(abcd.data.train.harmonized$PFN7,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN7,na.rm=TRUE)
abcd.data.train.harmonized$PFN8<-(abcd.data.train.harmonized$PFN8-mean(abcd.data.train.harmonized$PFN8,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN8,na.rm=TRUE)
abcd.data.train.harmonized$PFN9<-(abcd.data.train.harmonized$PFN9-mean(abcd.data.train.harmonized$PFN9,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN9,na.rm=TRUE)
abcd.data.train.harmonized$PFN10<-(abcd.data.train.harmonized$PFN10-mean(abcd.data.train.harmonized$PFN10,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN10,na.rm=TRUE)
abcd.data.train.harmonized$PFN11<-(abcd.data.train.harmonized$PFN11-mean(abcd.data.train.harmonized$PFN11,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN11,na.rm=TRUE)
abcd.data.train.harmonized$PFN12<-(abcd.data.train.harmonized$PFN12-mean(abcd.data.train.harmonized$PFN12,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN12,na.rm=TRUE)
abcd.data.train.harmonized$PFN13<-(abcd.data.train.harmonized$PFN13-mean(abcd.data.train.harmonized$PFN13,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN13,na.rm=TRUE)
abcd.data.train.harmonized$PFN14<-(abcd.data.train.harmonized$PFN14-mean(abcd.data.train.harmonized$PFN14,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN14,na.rm=TRUE)
abcd.data.train.harmonized$PFN15<-(abcd.data.train.harmonized$PFN15-mean(abcd.data.train.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN15,na.rm=TRUE)
abcd.data.train.harmonized$PFN16<-(abcd.data.train.harmonized$PFN16-mean(abcd.data.train.harmonized$PFN16,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN16,na.rm=TRUE)
abcd.data.train.harmonized$PFN17<-(abcd.data.train.harmonized$PFN17-mean(abcd.data.train.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN17,na.rm=TRUE)

abcd.data.test.harmonized$PFN1<-(abcd.data.test.harmonized$PFN1-mean(abcd.data.test.harmonized$PFN1,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN1,na.rm=TRUE)
abcd.data.test.harmonized$PFN2<-(abcd.data.test.harmonized$PFN2-mean(abcd.data.test.harmonized$PFN2,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN2,na.rm=TRUE)
abcd.data.test.harmonized$PFN3<-(abcd.data.test.harmonized$PFN3-mean(abcd.data.test.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN3,na.rm=TRUE)
abcd.data.test.harmonized$PFN4<-(abcd.data.test.harmonized$PFN4-mean(abcd.data.test.harmonized$PFN4,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN4,na.rm=TRUE)
abcd.data.test.harmonized$PFN5<-(abcd.data.test.harmonized$PFN5-mean(abcd.data.test.harmonized$PFN5,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN5,na.rm=TRUE)
abcd.data.test.harmonized$PFN6<-(abcd.data.test.harmonized$PFN6-mean(abcd.data.test.harmonized$PFN6,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN6,na.rm=TRUE)
abcd.data.test.harmonized$PFN7<-(abcd.data.test.harmonized$PFN7-mean(abcd.data.test.harmonized$PFN7,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN7,na.rm=TRUE)
abcd.data.test.harmonized$PFN8<-(abcd.data.test.harmonized$PFN8-mean(abcd.data.test.harmonized$PFN8,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN8,na.rm=TRUE)
abcd.data.test.harmonized$PFN9<-(abcd.data.test.harmonized$PFN9-mean(abcd.data.test.harmonized$PFN9,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN9,na.rm=TRUE)
abcd.data.test.harmonized$PFN10<-(abcd.data.test.harmonized$PFN10-mean(abcd.data.test.harmonized$PFN10,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN10,na.rm=TRUE)
abcd.data.test.harmonized$PFN11<-(abcd.data.test.harmonized$PFN11-mean(abcd.data.test.harmonized$PFN11,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN11,na.rm=TRUE)
abcd.data.test.harmonized$PFN12<-(abcd.data.test.harmonized$PFN12-mean(abcd.data.test.harmonized$PFN12,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN12,na.rm=TRUE)
abcd.data.test.harmonized$PFN13<-(abcd.data.test.harmonized$PFN13-mean(abcd.data.test.harmonized$PFN13,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN13,na.rm=TRUE)
abcd.data.test.harmonized$PFN14<-(abcd.data.test.harmonized$PFN14-mean(abcd.data.test.harmonized$PFN14,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN14,na.rm=TRUE)
abcd.data.test.harmonized$PFN15<-(abcd.data.test.harmonized$PFN15-mean(abcd.data.test.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN15,na.rm=TRUE)
abcd.data.test.harmonized$PFN16<-(abcd.data.test.harmonized$PFN16-mean(abcd.data.test.harmonized$PFN16,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN16,na.rm=TRUE)
abcd.data.test.harmonized$PFN17<-(abcd.data.test.harmonized$PFN17-mean(abcd.data.test.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN17,na.rm=TRUE)

abcd.data.train.harmonized$interview_age<-(abcd.data.train.harmonized$interview_age-mean(abcd.data.train.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.train.harmonized$interview_age,na.rm=TRUE)
abcd.data.test.harmonized$interview_age<-(abcd.data.test.harmonized$interview_age-mean(abcd.data.test.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.test.harmonized$interview_age,na.rm=TRUE)

abcd.data.train.harmonized$meanFD<-(abcd.data.train.harmonized$meanFD-mean(abcd.data.train.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.train.harmonized$meanFD,na.rm=TRUE)
abcd.data.test.harmonized$meanFD<-(abcd.data.test.harmonized$meanFD-mean(abcd.data.test.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.test.harmonized$meanFD,na.rm=TRUE)

abcd.data.train.harmonized$reshist_addr1_adi_income<-(abcd.data.train.harmonized$reshist_addr1_adi_income-mean(abcd.data.train.harmonized$reshist_addr1_adi_income,na.rm=TRUE))/sd(abcd.data.train.harmonized$reshist_addr1_adi_income,na.rm=TRUE)
abcd.data.test.harmonized$reshist_addr1_adi_income<-(abcd.data.test.harmonized$reshist_addr1_adi_income-mean(abcd.data.test.harmonized$reshist_addr1_adi_income,na.rm=TRUE))/sd(abcd.data.test.harmonized$reshist_addr1_adi_income,na.rm=TRUE)
```

@@

tab_model(mod4,mod5,mod6,pred.labels = c("Intercept","Age","Sex","Mean FD","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/Associations_TableX_Replication.doc")

# sensitivity analysis with ADI as an additional covariate:
mod101<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
mod102<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
mod103<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.train.harmonized)
mod104<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)
mod105<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)
mod106<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+reshist_addr1_adi_income+thompson_PC1,data=abcd.data.test.harmonized)

tab_model(mod101,mod102,mod103,pred.labels = c("Intercept","Age","Sex","Mean FD","ADI","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/ADI_Sensitivity_TableX_Discovery.doc")

tab_model(mod104,mod105,mod106,pred.labels = c("Intercept","Age","Sex","Mean FD","ADI","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/ADI_Sensitivity_TableX_Replication.doc")

@@

# Prep/add data for demographics table
```{r}

# exclude subjects with missing cognitive data
abcd.data.for.ridge<-abcd.data.traintest[,c("subjectkey","thompson_PC1","thompson_PC2","thompson_PC3","matched_group","interview_age","sex","meanFD","abcd_site","rel_family_id")]
abcd.data.traintest<-abcd.data.traintest[complete.cases(abcd.data.for.ridge),]

cbcl<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
cbcl_baseline <- cbcl[cbcl$eventname=="baseline_year_1_arm_1",c("subjectkey","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_totprob_r")]
cbcl_baseline$cbcl_scr_syn_internal_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_internal_r)
cbcl_baseline$cbcl_scr_syn_external_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_external_r)
cbcl_baseline$cbcl_scr_syn_totprob_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_totprob_r)

psychMed<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychotropicMeds/ABCD_Psychotropic_Medications.csv")
psychMed_baseline <- psychMed[psychMed$eventname=="baseline_year_1_arm_1",c("subjectkey","ADHD_meds","Antidepressant_meds","Antipsychotic_meds")]
psychMed_baseline$ADHD_meds<-as.factor(psychMed_baseline$ADHD_meds)
psychMed_baseline$Antipsychotic_meds<-as.factor(psychMed_baseline$Antipsychotic_meds)
psychMed_baseline$Antidepressant_meds<-as.factor(psychMed_baseline$Antidepressant_meds)

abcd.data.traintest<-merge(abcd.data.traintest,cbcl_baseline,by="subjectkey")
abcd.data.traintest<-merge(abcd.data.traintest,psychMed_baseline,by="subjectkey")

abcd.data.traintest$ADHD_meds<-factor(abcd.data.traintest$ADHD_meds, levels = c("1","0"))
abcd.data.traintest$Antidepressant_meds<-factor(abcd.data.traintest$Antidepressant_meds, levels = c("1","0"))
abcd.data.traintest$Antipsychotic_meds<-factor(abcd.data.traintest$Antipsychotic_meds, levels = c("1","0"))

# Make a demographics table
```{r}
library(Gmisc)
demo_table <- abcd.data.traintest %>%
  mutate(matched_group = factor(matched_group, levels = 1:2, labels = c("Discovery", "Replication"))) %>%
#subset(matched_group<3) %>%
  set_column_labels(interview_age = "Age (Months)",
                    sex = "Sex (F)",
                    race.6level = "Race",
                    household.income = "Household Income",
                    high.educ = "Parent Education",
                    thompson_PC1 = "General Cognition",
                    thompson_PC2 = "Executive Function",
                    thompson_PC3 = "Learning/Memory",
                    ADHD_meds = "ADHD Medications",
                    Antidepressant_meds = "Antidepressant Medication",
                    Antipsychotic_meds = "Antipsychotic Medication",
                    cbcl_scr_syn_internal_r = "CBCL Int.",
                    cbcl_scr_syn_external_r = "CBCL Ext.",
                    cbcl_scr_syn_totprob_r = "CBCL Prob.") %>%
getDescriptionStatsBy(interview_age,
                        sex,
                        thompson_PC1,
                        thompson_PC2,
                        thompson_PC3,
                        ADHD_meds,
                        Antidepressant_meds,
                        Antipsychotic_meds,
                        cbcl_scr_syn_external_r,
                        cbcl_scr_syn_internal_r,
                        cbcl_scr_syn_totprob_r,
                        household.income,
                        race.6level,
                        high.educ,
                        add_total_col = TRUE, statistics=TRUE,
                        by = matched_group)

@@

# Look for effects of SES on total cortical representation
```{r}
ADI_mod1<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.train.harmonized)
ADI_mod2<-lmer(reshist_addr1_adi_income~interview_age+sex+(1|rel_family_id)+meanFD+PFN1+PFN2+PFN3+PFN4+PFN5+PFN6+PFN7+PFN8+PFN9+PFN10+PFN11+PFN12+PFN13+PFN14+PFN15+PFN16+PFN17,data=abcd.data.test.harmonized)

tab_model(ADI_mod1,ADI_mod2,pred.labels = c("Intercept","Age","Sex","Motion","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17"),dv.labels=c("ADI (Discovery)","ADI (Replication)"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="bonferroni",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SES/ADI_by_PFN.doc")
```

@@

net_locs = c()
for (i in 1:17){
  net_locs <- c(net_locs,which(z_vec_sorted==i))
}

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_train)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- ifelse(keep_p==1,"solid","dashed");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + ylim(-8.5,5.5) +
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted)) 
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_Disc_Revision.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@

net_locs = c()
for (i in 1:17){
  net_locs <- c(net_locs,which(z_vec_sorted==i))
}

# Using 7 colors scheme for bar plot
# bar plot for cognition effects
data <- data.frame(CognitionEffects_Z = as.numeric(z_vec_pn_test)) 
data$EffectRank <- as.numeric(z_vec_sorted)
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
LineType <- ifelse(keep_p==1,"solid","dashed");
Fig <- ggplot(data, aes(EffectRank, CognitionEffects_Z)) +
  geom_bar(stat = "identity", fill=ifelse(keep_p==1,BorderColor,"#FFFFFF"), 
           colour = BorderColor, linetype = LineType, width = 0.8) + ylim(-8.5,5.5) + 
  labs(x = "Networks", y = expression(paste("Cognition Association (", italic("Z"), ")"))) + theme_classic() +
  theme(axis.text.x = ggtext::element_markdown(size= 27, color = BorderColor[net_locs]), 
        axis.text.y = ggtext::element_markdown(size= 33, color = "black"), 
        axis.title=ggtext::element_markdown(size = 33)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(net_locs),limits = as.character(z_vec_sorted)) 
Fig
ggsave('/Users/askeller/Documents/Kellernet_PrelimAnalysis/CuiRep_032322/NetworkSize_Loading_CogEffects_Rep_Revision.tiff', width = 19, height = 16, dpi = 600, units = "cm");

@@

# Test whether results hold with covariates for psychotropic med use:
```{r}
abcd.data.train.harmonized.withMeds <- merge(abcd.data.train.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.train.harmonized)))],by="subjectkey")
abcd.data.test.harmonized.withMeds <- merge(abcd.data.test.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.test.harmonized)))],by="subjectkey")

mod1<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
mod2<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
mod3<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.train.harmonized.withMeds)
mod4<-lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)
mod5<-lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)
mod6<-lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+ADHD_meds+Antipsychotic_meds+Antidepressant_meds+thompson_PC1,data=abcd.data.test.harmonized.withMeds)

tab_model(mod1,mod2,mod3,pred.labels = c("Intercept","Age","Sex","Mean FD","ADHD Meds","Antipsychotic Meds","Antidepressant Meds","General Cognition"),dv.labels=c("PFN 3","PFN 15","PFN 17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = "/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychMedUse/Associations_TableX_Disc_PsychMed.doc")
